\documentclass[10pt,twoside,openany]{book}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{lib/dnd}
\usepackage{listings}
\usepackage{multicol}
\usepackage{hyperref}

\title{Age of Vectron}
\author{Peter Cummuskey}
\date{November 2017}

\lstset{%
  basicstyle=\ttfamily,
  language=[LaTeX]{TeX},
}

\begin{document}

\maketitle

\chapter{Table of Contents}
\makeatletter
	\let\ps@plain\ps@fancy
	\@starttoc{toc}
\makeatother

\chapter{Introduction}
\begin{multicols}{2}

	% TODO

\end{multicols}

\chapter{Character Creation}
\begin{multicols}{2}

	In Age of Vectron, you take the role of a hero, someone who has
	been put at the reigns of destiny thanks to the circumstances of their
	birth, the patronage of dark gods, or simply dumb luck and an ability to
	capitalize in it. You are one in a million, with abilities and powers
	beyond those most can even imagine. Perhaps you'll seek out justice, or
	power, or just the cold comfort of gold.

	You and your Party, your fellow Heroes, will be faced with some
	of the greatest challenges in the Great Wheel, quests and opponents that
	would crush lesser men and nations alike. There is no hero who is
	unwilling or unable to use the power they wield - someone who shirks away
	from their desires and their destiny is unworthy of being a Hero.

	Despite all of your power and abilities, though, remember that
	it is not going to be an easy task to achieve your destiny. At the
	earliest stages, you will be little better than an experienced warrior,
	scholar, or thief. You'll need to use your wits, luck, and the skills of
	your companions to survive. The longer the last and the stronger you
	become, the greater the foes you will be asked to face. There has never
	been a hero who has known peace.

	When you die, you will be remembered. Perhaps for great deeds,
	perhaps for terrible ones, but there will be those who know your name.
	Your struggle, your triumph, your failure - these are the things that will
	become the legends of the next age.

	\section{Creating a Hero}

		To get started on your quest, you need to make your Hero,
		also known as your character (or Player Character, or PC). Creating
		your Player Character is a simple process that many people find fun in
		itself. As you go through this chapter, you'll find the tools to
		construct an interesting persona with a history, attachment to the
		world, and beliefs. Be aware, there may be many unfamiliar terms
		ahead, but have no fear - everything will get explained, if not here
		then in a later chapter as you explore the rest of this rulebook.

		Before you get started, you'll want to gather some supplies
		- a character sheet, a pencil, and an eraser. It's best to write
		everything in pencil to start with, as it's likely you'll end up
		changing or scrapping things as you go along. You may also like to
		have some spare scraps of paper to take notes. It's also useful to get
		together with the group you'll be playing with when you make your
		character, so you can make sure your Heros all complement one another.

		There are a number of simple steps you should follow
		whenever you are creating a new Hero. Each step is relatively simple,
		consisting of making a few choices and recording your selections onto
		your character sheet. Each stage in the character creation process is
		as follows.

	\section{Step 0: Character Concept}

		Before filling in even a single dot on your character
		sheet, think of a concept. You don't need to know every detail of your
		hero's life right now, just a general feel for who they are and their
		current place in the world. Decide on something you'll enjoy playing
		for the long haul. As you progress through character creation, you may
		alter this concept to suit your needs or wants, but it's a good idea
		to start somewhere instead of just picking things at random. Your
		Story Master may restrict some options, for example disallowing some
		races or Exaltations, so make sure they approve your concept.

	\section{Step 1: Choose you Exaltation}

	\section{Step 2: Choose your Race}

	\section{Step 3: Choose a Class}

	\section{Step 4: Spend Experience}

		\subsection{Attributes}

		\subsection{Skills}

		\subsection{Classes}

		\subsection{Perks}

		\subsection{Flaws}

	\section{Step 5: Purchase Equipment}

	\section{Step 6: Derive Statistics}

	\section{Step 7: Create History}

\end{multicols}

\chapter{Exaltations}
\begin{multicols}{2}

	\section{Atlanteans}

	\section{Chosen}

	\section{Daemonhost}

	\section{Dragonblooded}

	\section{Paragon}

	\section{Promethean}

	\section{Vampire}

	\section{Werewolf}

	\section{Wraith}

\end{multicols}

\chapter{Attributes and Skills}
\begin{multicols}{2}

	\section{Attributes}

	\section{Skills}

		\subsection{Specialties}

\end{multicols}

\chapter{Races}
\begin{multicols}{2}

	% TODO

\end{multicols}

\chapter{Classes}
\begin{multicols}{2}

	% TODO

\end{multicols}

\chapter{Feats}
\begin{multicols}{2}

	% TODO

\end{multicols}

\chapter{Equipment}
\begin{multicols}{2}

	% TODO

\end{multicols}

\chapter{Playing the Game}
\begin{multicols}{2}

	% TODO

\end{multicols}

\end{document}

